### 2018-12-18 README.Rmd
add example map to README and areal vig

>>>>

What results from `aw_interpolate()` is mapped below. Total population per census tract in St. Louis is mapped on the left in panel A. Using `aw_interpolate()` as we did in the previous example, we estimate population counts for Wards in St. Louis from those census tract values. These estimated values are mapped on the right in panel B.

```{r exampleMap, echo=FALSE, out.width = '100%'}
knitr::include_graphics("man/figures/exampleMap.png")
```

### 2018-12-18 index.Rmd
add example map to README and areal vig

## Resources
* The [Get started](/areal/) article has:
    * a quick overview of getting up and running with `areal` including **installation tips**,
    * some notes on **preparing data** for interpolation,
    * a brief introduction to the **`aw_interpolate()` function**,
    * tips for **getting help**, **submitting feedback**, 
    * and the `areal` package's development roadmap!
* Additional details about preparing data are available in a [dedicated article](/data-preparation/).
* The areal weighted interpolation process is described in-depth in a [dedicated article](/areal-weighted-interpolation/).

>>>>

## Resources
* The [Get started](articles/areal.html) article has:
    * a quick overview of getting up and running with `areal` including **installation tips**,
    * some notes on **preparing data** for interpolation,
    * a brief introduction to the **`aw_interpolate()` function**,
    * tips for **getting help**, **submitting feedback**, 
    * and the `areal` package's development roadmap!
* Additional details about preparing data are available in a [dedicated article](articles/data-preparation.html).
* The areal weighted interpolation process is described in-depth in a [dedicated article](articles/areal-weighted-interpolation.html).
